---
title: NEE flux tower reconciliation
---

```{r setup, include = FALSE}
library(tidyverse)
```

$$
NEE = GPP - R
$$

Therefore...

$$
GPP = NEE + R
$$

$$
R = R_a + R_h
$$

$$
R_a = R_{a,below} + R_{a,above}
$$

$$
R_{chamber} = R_{a,below} + R_h
$$

Let $f$ be the root contribution to $R_{chamber}$, such that:

$$
R_{a,below} = f R_{chamber}
$$

$$
R_h = (1 - f) R_{chamber}
$$

Let $\phi$ be the belowground fraction of autotrophic respiration, such that:

$$
R_{a,below} = \phi R_a
$$

$$
R_{a,above} = (1 - \phi) R_a
$$

Rearranging, we get:

$$
R_a = \frac{R_{a,above}}{1 - \phi}
$$

This leads to a complete model of GPP as:

$$
GPP = NEE + R_h + R_a
$$

...where

$$
R_h = (1 - f) * R_{chamber}
$$

...and...

$$
R_{a} = \frac{R_{a,below}}{1 - \phi}
$$

This creates a GPP model with 2 inputs---NEE (flux tower) and R~chamber~ (COSORE)---and 2 parameters (fraction of R~chamber~ from roots, $f$; fraction of autotrophic respiration aboveground, $\phi$):

```{r}
#' @param nee Flux tower net ecosystem exchange
#' @param r_chamber Respiration chamber measurement
#' @param phi aboveground fraction of autotrophic respiration
#' @param f belowground autotrophic fraction of chamber resp that 
gpp_r <- function(nee, r_chamber, phi, f) {
  r_h <- (1 - f) * r_chamber
  r_ab <- f * r_chamber
  r <- r_ab / (1 - phi) + r_h
  gpp <- nee + r
  return(gpp)
}
```

Define some prior distributions.

```{r}
par(mfrow = c(1, 2))
curve(dbeta(x, 2, 2), 0, 1, main = "f")
curve(dbeta(x, 2, 2), 0, 1, main = "phi")
```

Now, draw some parameters and do some simulations.

```{r}
n <- 10000

result <- tibble(
  method = "NEE",
  f = rbeta(n, 2, 2),
  phi = rbeta(n, 2, 2),
  gpp = gpp_r(6, 3, phi, f)
)

ggplot(result) +
  aes(x = gpp) +
  geom_density() +
  coord_cartesian(xlim = c(0, 50)) +
  theme_bw()
```

At the same time...

$$
GPP = m NIR_v + b
$$

```{r}
gpp_nirv <- function(nirv, m, b) {
  out <- m * nirv + b
  # Convert units
  # umol C m-2 s-1 to Mg ha-1 year-1
  out * 12 / 1e6 * (60 * 60 * 24 * 365) / 10000
}
```

Define priors on GPP parameters

```{r}
par(mfrow = c(1, 2))
curve(dexp(x, 0.5), 0, 8, main = "NIRv int.")
curve(dnorm(x, 65, 10), 30, 110, main = "NIRv slope")
```

Now, add the NIR~v~.

```{r}
result_nir <- tibble(
  method = "NIR",
  b = rexp(n, 0.5),
  m = rnorm(n, 65, 10),
  gpp = gpp_nirv(0.4, m, b)
)

result %>%
  bind_rows(result_nir) %>%
  ggplot(aes(x = gpp, fill = method)) +
  geom_density() +
  coord_cartesian(xlim = c(0, 50)) +
  theme_bw()
```
